Papers

### 2025-08-06 papers.qmd
update

@@

- - Boag, R. J., Innes, R. J., Stevenson, N., Bahg, G., Busemeyer, J. R., Cox, G. E., … Forstmann, B. (2024, July 2). [An expert guide to planning experimental tasks for evidence accumulation modelling](https://osf.io/preprints/psyarxiv/snqgp).

@@

>>>>

- Stafford, T., Zhu, J., & Dommett, K. (2024, December 31). Quantifying belief in the rationality of others: the Faith in Reason scale. Working Paper. <https://doi.org/10.31234/osf.io/umwxj>

@@

- Boag, R. J., Innes, R. J., Stevenson, N., Bahg, G., Busemeyer, J. R., Cox, G. E., ... & Forstmann, B. U. (2025). [An expert guide to planning experimental tasks for evidence-accumulation modeling](https://doi.org/10.1177/25152459251336127). Advances in Methods and Practices in Psychological Science, 8(2), 25152459251336127. <https://doi.org/10.1177/25152459251336127>

@@

- Myers, J. A., Stafford, T., Koychev, I., Perneczky, R., Bandmann, O., & Vaci, N. (2025). [Loneliness, social isolation, and effects on cognitive decline in patients with dementia: A retrospective cohort study using natural language processing](https://doi.org/10.1002/dad2.70149). Alzheimer's & Dementia: Diagnosis, Assessment & Disease Monitoring, 17(3), e70149. <https://doi.org/10.1002/dad2.70149>
